The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-01 eswc-2012/workshop2.tex
collapse hfactors
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@144 43ef1190-90fd-4dd7-a769-d0121f02b80e

We noted that for a read-write RESTful protocol, we need to say in the
RDF message itself what can of operations can be made. We also note
that only information resources can be manipulated, and we argued that
it should be possible to add the required triples to every
resource. We should be able to define hypermedia RDF in terms of a
minimal vocabulary, but like the H~Factor web page, we shall find it
instructive to use examples. In the following, we use Turtle syntax
with prefixes omitted for brevity. Also, we note that in many cases,
we are making statements about the current resource, which given a
reasonable base URI can be written as \texttt{<>}. These are the H~Factors:

\begin{description}
\item[LE] Support for embedded links (HTTP GET)

Not relevant for RDF.

\item[LO] Support for out-bound navigational links (HTTP GET)

Trivially supported by RDF.

\item[LT] Support for templated queries (HTTP GET)

Undefined by this paper. Possibly supported by RDForms\footnote{\url{http://vocab.deri.ie/rdforms}}?

\item[LN] Support for non-idempotent updates (HTTP POST)

@@

\item[LI] Support for idempotent updates (HTTP PUT, DELETE)

@@

\item[CR] Support for modifying control data for read requests
  (e.g. HTTP Accept-* headers).

@@

\item[CU] Support for modifying control data for update requests
  (e. g. Content-* headers).

Undefined by this paper.

\item[CM] Support for indicating the interface method for requests
  (e.g. HTTP GET, POST, PUT, DELETE methods).

@@

\item[CL] Support for adding semantic meaning to link elements using
  link relations (e.g. HTML rel attribute).

Trivially supported by RDF.

>>>>

We noted that for a read-write RESTful protocol, we need to say in the
RDF message itself what can of operations can be made. We also note
that only information resources can be manipulated, and we argued that
it should be possible to add the required triples to every
resource. We should be able to define hypermedia RDF in terms of a
minimal vocabulary, but like the H~Factor web page, we shall find it
instructive to use examples. In the following, we use Turtle syntax
with prefixes omitted for brevity. Also, we note that in many cases,
we are making statements about the current resource, which given a
reasonable base URI can be written as \texttt{<>}. We have not found
the following factors to be relevant to RDF: \textsf{LE}, \textsf{CU}
and \textsf{LT} (though the latter may be supported by
RDForms\footnote{\url{http://vocab.deri.ie/rdforms}}?)  Then
\textsf{LO} and \textsf{CL} are trivially supported. The remaining are:

\begin{description}

\item[\textsf{LN}] Support for non-idempotent updates (HTTP POST)

@@

\item[\textsf{LI}] Support for idempotent updates (HTTP PUT, DELETE)

@@

\item[\textsf{CR}] Support for modifying control data for read requests
  (e.g. HTTP Accept-* headers).

@@

\item[\textsf{CM}] Support for indicating the interface method for requests
  (e.g. HTTP GET, POST, PUT, DELETE methods).

@@
